Balsa: A Compact Line Notation Based on SMILES

### 2022-06-24 manuscript.tex
Adds electron counting figure. closes #1
Adds Figure: Dime. closes #2
Adds figure for perfect matching. closes #3

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Electron Counting. A root atom and its child are added to a tree (left). Next, a bond is added (center). Finally, the appropriate electron count is deducted from each atom and added to the bond (right).}
    \label{fig:electron-counting}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Delocalization-induced molecular equality (DIME). Two chemically equivalent molecular graphs differ on the basis of delocalization.}
    \label{fig:dime}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Perfect Matching. A subgraph with all of the nodes of its parent, but in which all nodes have degree one.}
    \label{fig:perfect-matching}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{electron-counting.pdf}
    \caption{Electron Counting. A root atom and its child are added to a tree (left). Next, a bond is added (center). Finally, the appropriate electron count is deducted from each atom and added to the bond (right).}
    \label{fig:electron-counting}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=2in]{dime.pdf}
    \caption{Delocalization-induced molecular equality (DIME). Two chemically equivalent molecular representations differ only due to delocalization.}
    \label{fig:dime}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{matching.pdf}
    \caption{Perfect Matching. A matching is a subgraph in which all nodes have degree one. A perfect matching contains all of the nodes of its parent. Nodes and edges of a matching are noted with black circles and hashed lines, respectively. The five-membered cycle on the left has no perfect matching. Such graphs are not valid delocalization subgraphs. The six-membered cycle on the right has a perfect matching, and would be a valid delocalization subgraph. Either graph or tree representation can be used to construct a perfect matching, but published algorithms use graphs.}
    \label{fig:perfect-matching}
\end{figure}
